Hector Permafrost

### 2020-03-17 analysis/paper/paper.Rmd
Add missing packages for paper.Rmd & other fixes

```{r setup, echo = FALSE}
library(knitr)
library(here)
library(dplyr)
library(ggplot2)

@@

pkgload::load_all(here())
pkgload::load_all("~/Projects/hector_project/hector-permafrost-submodel")

@@

run_rcp <- function(rcp) {
  inidir <- file.path("~", "Projects", "hector_project",
                      "hector-permafrost-submodel", "inst", "input")
  inifile <- normalizePath(file.path(inidir, paste0("hector_rcp", rcp, ".ini")))
  stopifnot(file.exists(inifile))
  hc <- newcore(inifile)
  dates <- seq(1750, 2100)
  run(hc, max(dates))
  outvars <- c(ATMOSPHERIC_CO2(), GLOBAL_TEMP(), F_FROZEN(), SOIL_C())
  no_pf <- fetchvars(hc, dates, outvars, scenario = "Original")
  reset(hc)
  setvar(hc, 0, PERMAFROST_C(), 1035, "PgC")
  run(hc, max(dates))
  yes_pf <- fetchvars(hc, dates, outvars, scenario = "Permafrost")
  return(tibble::as_tibble(dplyr::bind_rows(no_pf, yes_pf)))
}

>>>>

```{r setup, echo = FALSE}
library(knitr)
library(here)
library(dplyr)
library(ggplot2)
library(hector)

@@

pkgload::load_all(here())

@@

run_rcp <- function(rcp) {
  inidir <- system.file("input", package = "hector")
  inifile <- normalizePath(file.path(inidir, paste0("hector_rcp", rcp, ".ini")))
  stopifnot(file.exists(inifile))
  hc <- newcore(inifile)
  dates <- seq(1750, 2100)
  run(hc, max(dates))
  outvars <- c(ATMOSPHERIC_CO2(), GLOBAL_TEMP(), F_FROZEN(), SOIL_C())
  no_pf <- fetchvars(hc, dates, outvars, scenario = "Original")
  reset(hc)
  setvar(hc, 0, PERMAFROST_C(), 1035, "PgC")
  run(hc, max(dates))
  yes_pf <- fetchvars(hc, dates, outvars, scenario = "Permafrost")
  return(tibble::as_tibble(dplyr::bind_rows(no_pf, yes_pf)))
}
